\chapter{Gospel Related Questions}

\paragraph{A people prepared for the Lord}
In Luke 1:17 the angel Gabriel tells Zacharias that his son, John the Baptist, would "make ready a people prepared for the Lord."
\begin{enumerate}
  \item What attributes does a people prepared for the Lord have?
  \item What does it mean to be prepared for the Lord's coming?
  \item What did God do to prepare the people for Christ's first coming?
\end{enumerate}

\paragraph{Having had a great knowledge of the goodness of God}
Nephi opens his writings by saying that he "had a great knowledge of the goodness and the mysteries of God...."
\begin{enumerate}
  \item How did Nephi gain this knowledge?
\end{enumerate}

Possible clues \begin{enumerate}
  \item His parents taught him true and eternal principles.
  \item He experienced many afflictions.
\end{enumerate}

Yet, in spite of the afflictions that Nephi experienced, he was still able to say that he was "highly favored of the Lord in all [his] days."

\paragraph{Gospel fruit}
He spake this parable; A certain man had a fig tree planted in his vineyard; and he came and sought fruit thereon, and found none.

Then said he unto the dresser of his vineyard, Behold, these three years I come seaking fruit on this fig tree, and fine none: cut it down; why cumbreth it the ground?

And he answering said unto him, Lord, let it alone this year also, till I shall dig about it, and dung it:

And if it bear fruit, well: and if not, then after that thou shalt cut it down. (Luke 13:6-9)

\textbf{Question} What is the \emph{fruit} that the Lord seeks from us?

I think it can be easy to equate fruit with works and I don't think that's the kind of fruit the Lord is after. I think the fruit the Savior is speaking of are attributes that He would like us to develop through effort and intention. For example, things like being
\begin{enumerate}
  \item humble
  \item patient
  \item teachable
  \item faithful
  \item kind
\end{enumerate}

