\chapter{Acts and Words of Jesus Christ}

\section{Prior to the start of His ministry}

\paragraph{Baptism}
And it came to pass in those days, that Jesus came from Nazareth of Galilee, and was baptized of John in Jordan. (Mark 1:9)

\paragraph{Preparation in the Wilderness}
And immediately\footnote{after being baptized} the Spirit driveth him into the wilderness. And he was there in the wilderness forty days, tempted of Satan; and was with the wild beasts; and the angels ministered unto him. (Mark 1:12-13)

\paragraph{Preaching the gospel}
Now after that John was put in prison, Jesus came into Galilee, preaching the gospel of the kingdom of God, And saying, The time is fulfilled, and the kingdom of God is at hand: repent ye, and believe the gospel. (Mark 1:14-15)

\section{Calling His Apostles}

\paragraph{Simon and Andrew}
Now as he walked by the sea of Galilee, he saw Simon and Andrew his brother casting a net into the sea; for they were fishers. And Jesus said unto them, Come ye after me, and I will make you to become fishers of men. (Mark 1:16-17)

\paragraph{James and John}
And when he had gone a little further thence, he saw James the son of Zebedee, and John his brother, who also were in the ship mending their nets. And straightway he called them: and they left their father Zebedee in the ship with the hired servants, and went after him. (Mark 1:19-20)

\section{Teaching}
And they went into Capernaum;\footnote{this is the first thing Mark says He did after calling Simon, Andrew, James, and John} and straightway on the sabbath day he entered into the synagogue, and taught. And they were astonished at his doctrine: for he taught them as one that had authority, and not as the scribes. (Mark 1:21-22)

\section{Miracles}

\paragraph{He did not many mighty works}
And when he was come into his own country, he taught them in their synagogue, insomuch that they were astonished, and said, Whence hath this man this wisdom, and these mighty works? Is not this the carpenter's son? ... And they were offended in him. But Jesus said unto them, A prophet is not without honor, save in his own country, and in his own house. And he did not many mighty works there because of their unbelief. (Matthew 13:54-58)

