\chapter{The Second Coming of Jesus Christ}


\section{The preparation}

\begin{quotation}
Behold, I will send my messenger, and he shall prepare the way before me: and the Lord, whom ye seek, shall suddenly come to his temple, even the messenger of the covenant, whom ye delight in: behold, he shall come, saith the Lord of hosts. (Malachi 3:1)
\end{quotation}

\begin{quotation}
Behold, I will send you Elijah the prophet before the coming of the great and dreadful day of the Lord: And he shall turn the heart of the fathers to the children, and the heart of the children to their fathers, lest I come and smite the earth with a curse. (Malachi 4:5-6)
\end{quotation}

\begin{quotation}
And he [John the Baptist] shall go before him [the Lord] in the spirit and power of Elias, to turn the hearts of the fathers to the children, and the disobedient to the wisdom of the just; to make ready a people prepared for the Lord. (Luke 1:17)\footnote{I know this verse is about the Messiah's first coming, but I can't help but think that a similar preparation needs to occur before His second coming. What does a people 'prepared for the Lord' look like?}
\end{quotation}


\section{The gathering}

\begin{quotation}
And I will remember the covenant which I have made with my people; and I have covenanted with them that I would gather them together in mine own due time, that I would give unto them again the land of their fathers for their inheritance, which is the land of Jerusalem, which is the promised land unto them forever, saith the Father (3 Nephi 20:29).
\end{quotation}

\begin{quotation}
Then will the Father gather them together again, and give unto them Jerusalem for the land of their inheritance (3 Nephi 20:33).
\end{quotation}

\begin{quotation}
And it shall come to pass in that day, that the remnant of Israel, and such as are escaped of the house of Jacob, shall no more again stay upon him that smote them; but shall stay upon the Lord, the Holy One of Israel, in truth. The remnant shall return, even the remnant of Jacob, unto the mighty God (Isaiah 10:20-21, 2 Nephi 20:20-21).
\end{quotation}

\section{The refiner's fire}

\begin{quotation}
But who may abide the day of his coming? and who shall stand when he appeareth? for he is like a refiner's fire, and like a fuller's soap: And he shall sit as a refiner and purifier of silver: and he shall purify the sons of Levi, and purge them as gold and silver, that they may offer unto the Lord an offering in righteousness. (Malachi 1:2-3)
\end{quotation}

\begin{quotation}
For, behold, the day cometh that shall burn as an oven; and all the proud, yea, and all that do wickedly, shall be as stubble: and the day that cometh shall burn them up, saith the Lord of hosts, that it shall leave them neither root nor branch. (Malachi 4:1)
\end{quotation}

\begin{quotation}
Then shall the offering of Judah and Jerusalem be pleasant unto the Lord, as in the days of old, and as in former years.(Malachi 1:4)
\end{quotation}

\begin{quotation}
Yea, the day of the Lord shall come upon all the cedars of Lebanon, for they are high and lifted up; and upon all the oaks of Bashan; And upon all the high mountains, and upon all the hills, and upon all the nations which are lifted up, and upon every people. And upon every high tower, and upon every fenced wall; And upon all the ships of the sea, and upon all the ships of Tarshish, and upon all pleasant pictures. And the loftiness of man shall be bowed down, and the haughtiness of men shall be made low; and the Lord alone shall be exalted in that day (2 Nephi 12:13-17; Isaiah 2:13-17).
\end{quotation}

\begin{quotation}
And the idols he shall utterly abolish. And they shall go into the holes of the rocks, and into the caves of the earth, for the fear of the Lord shall come upon them and the glory of his majesty shall smite them, when he ariseth to shake terribly the earth. In that day a man shall cast his idols of silver, and his idols of gold, which he hath made for himself to worship, to the moles and to the bats; To go into the clefts of the rocks, and into the tops of the ragged rocks, for the fear of the Lord shall come upon them and the majesty of his glory shall smite them, when he ariseth to shake terribly the earth (2 Nephi 12:18-21; Isaiah 2:18-21).
\end{quotation}


\section{A judgement}

\begin{quotation}
And I will come near to you to judgment; and I will be a swift witness against the sorcerers, and against the adulterers, and against false swearers, and against those that oppress the hireling in his wages, the widow, and the fatherless, and that turn aside the stranger from his right, and fear not me, saith the Lord of hosts. (Malachi 3:5)
\end{quotation}

\begin{quotation}
In that day shall the branch of the Lord be beautiful and glorious, and the fruit of the earth shall be excellent and comely for them that are escaped of Israel. And it shall come to pass, that he that is left in Zion, and he that remaineth in Jerusalem, shall be called holy, even every one that is written among the living in Jerusalem: When the Lord shall have washed away the filth of the daughters of Zion, and shall have purged the blood of Jerusalem from the midst thereof by the spirit of judgment, and by the spirit of burning (Isaiah 4:2-4).
\end{quotation}

\begin{quotation}
And with righteousness shall the Lord God judge the poor, and reprove with equity for the meek of the earth. And he shall smite the earth with the rod of his mouth; and with the breath of his lips shall he slay the wicked (2 Nephi 30:9).
\end{quotation}

\begin{quotation}
For the time speedily cometh that the Lord God shall cause a great division among the people, and the wicked will he destroy; and he will spare his people, yea, even if it so be that he must destroy the wicked by fire (2 Nephi 30:10).
\end{quotation}


\section{The righteous}

\begin{quotation}
Then they that feared the Lord spake often one to another: and the Lord hearkened, and heard it, and a book of rememberance was written before him for them that feared the Lord, and that thought upon his name. And they shall be mine, saith the Lord of hosts, in that day when I make up my jewels; and I will spare them, as a man spareth his own son that serveth him. (Malachi 3:16-17)
\end{quotation}

\begin{quotation}
But unto you that fear my name shall the Sun of righteousness arise with healing in his wings; and ye shall go forth, and grow up as calves in the stall. And ye shall tread down the wicked; for they shall be ashes under the soles of your feet in the day that I shall do this, saith the Lord of hosts. (Malachi 4:2-3)
\end{quotation}

\begin{quotation}
In that day shall the branch of the Lord be beautiful and glorious, and the fruit of the earth shall be excellent and comely for them that are escaped of Israel. And it shall come to pass, that he that is left in Zion, and he that remaineth in Jerusalem, shall be called holy, even every one that is written among the living in Jerusalem: When the Lord shall have washed away the filth of the daughters of Zion, and shall have purged the blood of Jerusalem from the midst thereof by the spirit of judgment, and by the spirit of burning (Isaiah 4:2-4).
\end{quotation}

\begin{quotation}
And the Lord will create upon every dwelling place of mount Zion, and upon her assemblies, a cloud and smoke by day, and the shining of a flaming fire by night: for upon all the glory shall be a defence. And there shall be a tabernacle for a shadow in the daytime from the heat, and for a place of refuge, and for a covert from storm and from rain (Isaiah 4:5-6).
\end{quotation}


\section{Revelation}

\begin{quotation}
Wherefore, the things of all nations shall be made known; yea, all things shall be made known unto the children of men. There is nothing which is secret save it shall be revealed; there is no work of darkness save it shall be made manifest in the light; and there is nothing which is sealed upon the earth save it shall be loosed. Wherefore, all things which have been revealed unto the children of men shall at that day be revealed; (2 Nephi 30:16-18)
\end{quotation}
