\chapter{Testimonies of Jesus Christ}

\section{Old Testament}

\paragraph{Out of thee shall come forth unto me a ruler in Israel}
But thou, Beth-lehem Ephratah, though thou be little among the thousands of Judah, yet out of thee shall come forth unto me that is to be ruler in Israel; whose goings forth have been from of old, from everlasting. (Micah 5:2)\index{Micah 5:2}

\paragraph{I called my son out of Egypt}
When Israel was a child, then I loved him, and called my son out of Egypt. (Hosea 11:1)\footnote{Matthew interprets this verse to be referring to the Messiah and the time He spent in Egypt as a young child as a fulfillment of this prophecy. Traditionally, Hosea's prophecy is thought to refer to the exodus of Israel from Egypt.}

\section{Of His Divine Birth}

\paragraph{Where is he that is born King of the Jews?}
Now when Jesus was born in Bethlehem of Judaea in the days of Herod the king, behold, there came wise men from the east to Jerusalem, Saying, Where is he that is born King of the Jews? for we have seen his star in the east, and are come to worship him. (Matthew 2:1-2)

\paragraph{in Bethlehem, for thus it is written by the prophet}
When Herod the king had heard all these things, he was troubled, and all Jerusalem with him. And when he had gathered all the chief priests and scribes of the people\footnote{the Sanhedrin} together, he demanded of them where Christ should be born. And they said unto him, In Bethlehem of Judaea: for thus it is written by the prophet.\footnote{Micah 5:2} (Matthew 2:3-5)

\paragraph{Shall not Christ come out of Bethlehem?}
Hath not the scripture said, That Christ cometh of the seed of David, and out of the town of Bethlehem, where David was? (John 7:42)\footnote{This question is asked by the people in Jerusalem during the Feast of Tabernacles (Sukot) and shows that it was common knowledge at the time that the Messiah would be born in Bethlehem.}

\paragraph{and departed into Egypt}
When he arose, he took the young child and his mother by night, and departed into Egypt: And was there until the death of Herod: that it might be fulfilled which was spoken of the Lord by the prophet,\footnote{Hosea 11:1} saying, Out of Egypt have I called my son. (Matthew 2:14-15)

\paragraph{Gabriel to Mary}
Fear not, Mary: for thou has found favour with God. And, behold, thou shalt conceive in thy womb, and bring forth a son, and shalt call his name Jesus. He shall be great, and shall be called the Son of the Highest, and the Lord God shall give unto him the throne of his father David: And he shall reign over the house of Jacob for ever; and of his kingdom there shall be no end. (Luke 1:30-33)

And the angel answered and said unto her, The Holy Ghost shall come upon thee, and the power of the Highest shall overshadow thee: therefore also that holy thing which shall be born of thee shall be called the Son of God. (Luke 1:35)

\paragraph{Zacharias}
Blessed be the Lord God of Israel; for he hath visited and redeemed his people, and hath raised up an horn of salvation for us in the house of his servant David; ... To perform the mercy promised to our fathers, and to remember his holy covenant. The oath which he sware to our father Abraham. That he would grant unto us, that we being delivered out of the hand of our enemies might serve him without fear, in holiness and righteousness before him, all the days of our life. (Luke 1:68-69, 72-75)

\paragraph{Angels and Choirs in Heaven}
And the angel said unto them, Fear not: for, behold, I bring you good tidings of great joy, which shall be to all people. For unto you is born this day in the city of David a Saviour, which is Christ the Lord. (Luke 2:10-11)

\paragraph{Shepherds}
And it came to pass, as the angels were gone away from them into heaven, the shepherds said one to another, Let us now go even unto Bethlehem, and see this thing which is come to pass, which the Lord hath made known unto us. And they came with haste, and found Mary, and Joseph, and the babe lying in a manger. And when they had seen it, they made known abroad the saying which was told them concerning this child. (Luke 2:15-17)

\paragraph{Simeon}
And, behold, there was a man in Jerusalem, whose name was Simeon; and the same man was a just and devout, waiting for the consolation of Israel: and the Holy Ghost was upon him. And it was revealed unto him by the Holy Ghost, that he should not see death, before he had seen the Lord's Christ. And he came by the spirit into the temple: and when the parents brought in the child Jesus... Then took he him up in his arms, and blessed God, and said, (Luke 2:25-28)

Lord, now lettest thou thy servant depart in peace, according to thy word: For mine eyes have seen thy salvation, Which thou hast prepared before the face of all people; A light to lighten the Gentiles, and the glory of thy people Israel. (Luke 2:29-32)

And Simeon blessed them, and said unto Mary his mother, Behold, this child is set for the fall and rising again of many in Israel; and for a sign which shall be spoken against; (Yea, a sword shall pierce through thy own soul also,) that the thoughts of many hearts may be revealed. (Luke 2:34-35)

\paragraph{Anna}
And there was one Anna, a prophetess... which departed not from the temple, but served God with fastings and prayers night and day. And she coming in that instant gave thanks likewise unto the Lord, and spake of him to all them that looked for redemption in Jerusalem. (Luke 2:36-38)

\paragraph{Teachers in the Temple}
And it came to pass, that after three days they found him in the temple, sitting in the midst of the doctors, both hearing them, and asking them questions. And all that heard him were astonished at his understanding and answers. (Luke 2:46-47)

\paragraph{Jesus as a young man}
And he said unto them, How is it that ye sought me? wist ye not that I must be about my Father's business? (Luke 2:49)

\paragraph{Luke}\footnote{this knowledge probably came from someone like Mary who knew Jesus as a child}
And Jesus increased in wisdom and stature, and in favour with God and man. (Luke 2:52)

\section{Of His Divine Mission}

\paragraph{John the Baptist}
The next day John seeth Jesus coming unto him, and saith, Behold the Lamb of God, which taketh away the sin of the world. This is he of whom I said, After me cometh a man which is preferred before me: for he was before me. (John 1:29-30)

And John bare record, saying I saw the Spirit descending from heaven like a dove, and it abode upon him. And I knew him not:\footnote{this is the second time John says this. The first is in verse 31. In both I believe John is saying that he did not know who the Messiah was but that God had revealed to him that the Messiah would be manifest to Israel and that the Messiah would have power to baptize with the Holy Ghost.} but he that sent me to baptize with water, the same said unto me, Upon whom thou shalt see the Spirit descending, and remaining on him, the same is he which baptizeth with the Holy Ghost. And I saw, and bare record that this is the Son of God. (John 1:32-34)\footnote{John 1:19-34 provide evidence that the Jews believed in baptism of water and baptism of the Holy Ghost, or at least some of them did at the time of Jesus' life on earth.}

I indeed baptize you with water unto repentence: but he that cometh after me is mightier than I, whose shoes I am not worthy to bear: he shall baptize you with the Holy Ghost, and with fire: Whose fan is in his hand, and he will thoroughly purge his floor, and gather his wheat into the garner; but he will burn up the chaff with unquenchable fire. (Matthew 3:11-12) (See also Mark 1:7-8)

\paragraph{Andrew (brother of Simon Peter}
He first findeth his own brother Simon, and saith unto him, We have found the Messias, which is, being interpreted, the Christ. And he brought him to Jesus.... (John 1:41-42)

\paragraph{Philip}
Philip findeth Nathanael, and saith unto him, We have found him, of whom Moses in the law, and the prophets did write, Jesus of Nazareth, the son of Joseph. (John 1:45)

\paragraph{Nathanael}
Nathanael answered and saith unto him, Rabbi, thou art the Son of God; thou art the King of Israel. (John 1:49)

\paragraph{The Heavans and the Holy Ghost}
And Jesus, when he was baptized, went up straightway out of the water: and, lo, the heavens were opened unto him, and he saw the Spirit of God descending like a dove, and lighting upon him: (Matthew 3:16) (Mark 1:10)

\paragraph{Heavenly Father}
And lo a voice from heaven, saying, This is my beloved Son, in whom I am well pleased. (Matthew 3:17) (Mark 1:11)

\paragraph{An unclean spirit}
And there was in their synagogue a man with an unclean spirit; and he cried out, Saying let us alone; what have we to do with thee, thou Jesus of Nazareth? art thou come to destroy us? I know thee who thou art, the Holy One of God. (Mark 1:23-24)

\paragraph{A leper in Galilee}
If thou wilt, thou canst make me clean. (Mark 1:40)

\section{Opportunities for becoming converted}

\paragraph{They were all amazed}
And they were all amazed,\footnote{Jesus had just preached boldly in a synagogue in Capernaum and had cast an evil spirit out of someone in the synagogue} insomuch that they questioned among themselves, saying, What thing is this? what new doctrine is this? for with authority commandeth he even the unclean spirits, and they do obey him. (Mark 1:27)

\paragraph{They came to him from every quarter (to be healed)}
But he\footnote{the healed leper from verses 40-43} went out, and began to publish it much, and to blaze abroad the matter, insomuch that Jesus could no more openly enter into the city, but was without in desert places: and they came to him from every quarter. (Mark 1:45)
