\chapter{Words of Jesus Christ}

\section{New Testament}

\paragraph The time is fulfilled, and the kingdom of God is at hand: repent ye, and believe the gospel. (Mark 1:15)

\paragraph Come ye after me, and I will make you to become fishers of men. (Mark 1:17)

\paragraph Follow me, and I will make you fishers of men. (Matthew 4:19)

\paragraph Hold thy peace, and come out of him. (Mark 1:25)

\paragraph Let us go into the next towns, that I may preach there also; for therefore came I forth. (Mark 1:38)

\paragraph I will; be thou clean. (Mark 1:41)

\paragraph Follow me. (Luke 5:27)

\paragraph It is written, Man shall not live by bread alone, but by every word that proceedeth out of the mouth of God. (Matthew 4:4) (Luke 4:4)

It is written again, Thou shalt not tempt the Lord thy God. (Matthew 4:7) (Luke 4:12)

Get thee hence, Satan: for it is written, Thou shalt worship the Lord thy God, and him only shalt thou serve. (Matthew 4:10) (Luke 4:8)

\paragraph Woman, what have I to do with thee? mine hour is not yet come. (John 2:4)

Fill the waterpots with water. (John 2:7)

Draw out now, and bear unto the governor of the feast. (John 2:8)

\paragraph Take these things hence; make not my Father's house an house of merchandise. (John 2:16)

\paragraph Destroy this temple, and in three days I will raise it up. (John 2:19)

\paragraph Verily, verily, I say unto thee, Except a man be born again, he cannot see the kingdom of God. (John 3:3)

\paragraph Verily, verily, I say unto thee, Except a man be born of water and of the Spirit, he cannot enter into the kingdom of God.

That which is born of the flesh is flesh; and that which is born of the spirit is spirit.

Marvel not that I said unto thee, Ye must be born again.

The wind bloweth where it listeth, and thou hearest the sound thereof, but canst not tell whence it cometh, and whither it goeth: so is every one that is born of the Spirit. (John 3:5-8)

\paragraph{} Art thou a master of Israel, and knowest not these things\footnote{Jesus implies this should  have been common knowledge}?

Verily, verily, I say unto thee, We speak that we do know, and testify that we have seen; and ye receive our witness.

If I have told you earthly things, and ye believe not, how shall ye believe, if I tell you of heavenly things?

And no man hath ascended up to heaven, but he that came down from heaven, even the Son of man\index{Jesus Christ!names of!Son of man} which is in heaven.

And as Moses lifted up the serpent in the wilderness, even so must the Son of man be lifted up: That whosoever believeth in him should not perish, but have eternal life.

For God so loved the world, that he gave his only begotten Son, that whosoever believeth in him should not perish, but have everlasting life. 

For God sent not his Son into the world to condemn the world; but that the world through him might be saved.\index{Jesus Christ!mission of}

\paragraph The spirit of the Lord is upon me, because he hath anointed me to preach the gospel to the poor; he hath sent me to heal the broken-hearted, to preach deliverance to the captives, and recovering of sight to the blind, to set at liberty them that are bruised, To preach the acceptable year of the Lord.\footnote{perhaps referring to the Year of Jubilee, in which slaves are freed and debts are forgiven as prescribed in Leviticus 25:8-13} (Luke 4:18-19)

This day is this scripture fulfilled in your ears. (Luke 4:21)

Ye will surely say unto me this proverb, Physician, heal thyself: whatsoever we have heard done in Capernaum, do also here in thy country. (Luke 4:23)

Verily I say unto you, No prophet is accepted in his own country. But I tell you of a truth, many widows were in Israel in the days of Elias,\footnote{Greek for of Elijah} when the heaven was shut up three years and six months, when great famine was throughout all the land; But unto none of them was Elias\footnotemark[\value{footnote}] sent, save unto Sarepta, a city of Sidon, unto a woman that was a widow. And many lepers were in Israel in the time of Eliseus\footnote{Greek form of Elisha} the prophet; and none of them was cleansed saving Naaman the Syrian. (Luke 4:24-27)

\paragraph Man, thy sins are forgiven thee. What reason ye in your hearts? Whether it is easier to say, Thy sins be forgiven thee; or to say, Rise up and walk? But that ye may know that the Son of man hath power upon earth to forgive sins, I say unto thee, Arise, and take up thy couch, and go into thine house. (Luke 5:20, 22-24) (Mark 2:2-11)

\paragraph They that are whole need not a physician; but they that are sick. I came not to call the righteous, but sinners to repenentence. (Luke 5:31-32) (Mark 2:14-17)

\paragraph Can you make the children of the bridechamber fast, while the bridegroom is with them? But the days will come, when the bridegroom shall be taken away from them, and then shall they fast in those days. (Luke 5:34-35)

\paragraph I will; be thou clean. (Matthew 8:3) \index{faith}

\paragraph I have not found so great faith, no, not in Israel. Go thy way; and as thou has believed, so be it done unto thee. (Matthew 8:10, 13) \index{faith}

\paragraph The foxes have holes, and the birds of the air have nests; but the Son of man hath not where to lay his head. (Matthew 8:20) \index{discipleship!earthly rewards of}

\paragraph Follow me; and let the dead bury their dead.\footnote{I wonder if we really understand what this means. It seems like this teaching could be used to justify a very militaristic or robotic approach to discipleship.} (Matthew 8:22) \index{discipleship}

\paragraph Why are ye fearful, O ye of little faith? (Matthew 8:26) \index{faith} \index{fear}

\paragraph Have ye never read what David did, when he had need, and was an hungered, he and they that were with him? How he went into the house of God in the days of Abiathar the high priest, and did eat the shewbread, which is not lawful to eat but for the priests, and gave also to them which were with him? The sabbath was made for man, and not man for the sabbath: Therefore the Son of man is Lord also of the sabbath. (Mark 2:25-28)
